Reducing retrieval error in MAIAC AOD with the `Earth_obs_cleaning` machine-learning workflow: Results from CONUS

### 2023-08-23 writing/CONUS_AOD.qmd
Targetized more plots.

```{r basics}
source.files = "globals libraries util data modeling paper_functions"
for (filename in strsplit(source.files, " ")[[1]])
     source(sprintf("code/%s.R", filename))
suppressPackageStartupMessages(
   {library(patchwork)
    library(ggridges)
    library(kableExtra)
  })
the.sat = tools::toTitleCase(Wf$satellite)
```

@@

```{r agreement_plot}
knitr::include_graphics(targets::tar_read(agreement.plot.path))
```

@@

```{r shap_summary, dev='png', dpi=300}
shap_long <- shap.prep(shap_contrib = cv$shap_score,
                       X_train = cv$mDT_wPred[, names(cv$shap_score), with = F])
# **SHAP summary plot**
shap.plot.summary(shap_long)
```

```{r shap_features, dev='png', dpi=300}
g1 <- shap.plot.dependence(data_long = shap_long, x = 'time.sat', y = 'Column_WV', color_feature = 'Column_WV') +
    aes(x = lubridate::as_datetime(x_feature)) +
    xlab("time.sat") +
    ggtitle("(A) SHAP values of Column WV vs. Time trend")
# g2 <- shap.plot.dependence(data_long = shap_long, x = 'time.sat', y = 'y.sat', color_feature = 'y.sat') +  ggtitle("(B) SHAP values of MAIAC AOD vs. Time trend")
#
# gridExtra::grid.arrange(g1, g2, ncol = 2)
g1
```

@@

```{r pred.map.median.mse}
pred.map(
    tar_read(median.mse.map.data)$pred, tar_read(pred.grid),
    bg.sf = get_conus(), color.scale.name = "AOD",
    quantile.cap = .99)
```

@@

```{r pred.map.baltimore}
pred.map(
    tar_read(baltimore.map.data), tar_read(pred.grid),
    bg.sf = get_conus(), color.scale.name = "AOD")
```

>>>>

```{r basics}
source.files = "globals libraries util data modeling paper_functions"
for (filename in strsplit(source.files, " ")[[1]])
     source(sprintf("code/%s.R", filename))
suppressPackageStartupMessages(
   {library(patchwork)
    library(ggridges)
    library(kableExtra)
  })
the.sat = tools::toTitleCase(Wf$satellite)
IG = knitr::include_graphics
```

@@

```{r agreement_plot}
IG(tar_read(agreement.plot.path))
```

@@

```{r shap_summary}
IG(tar_read(shap.summary.plot.path))
```

```{r shap_features}
IG(tar_read(shap.features.plot.path))
```

@@

```{r pred.map.median.mse}
IG(tar_read(pred.map.median.mse.path))
```

@@

```{r pred.map.baltimore}
IG(tar_read(pred.map.baltimore.path))
```
